Supporting Information

### 2018-04-17 SupportingInformation.Rmd
modify tables

 atdres<-data.frame(Statistic=c("$\\cor_{0,0.1}-\\cor_{0.9,1}$","$\\Ps_{0,0.1}-\\Ps_{0.9,1}$","$\\Dsq_{0.9,1}-\\Dsq_{0,0.1}$"),
                   Kendall=rep("",3),
                   Spearman=rep("",3),stringsAsFactors = F)

>>>>

 #atdres<-data.frame(Statistic=c("$\\cor_{0,0.1}-\\cor_{0.9,1}$","$\\Ps_{0,0.1}-\\Ps_{0.9,1}$","$\\Dsq_{0.9,1}-\\Dsq_{0,0.1}$"),
 atdres<-data.frame(Statistic=c("$\\cor_{first.slice}-\\cor_{last.slice}$",
                                "$\\Ps_{first.slice}-\\Ps_{last.slice}$",
                                "$\\Dsq_{first.slice}-\\Dsq_{last.slice}$"),
                   Kendall=rep("",3),
                   Spearman=rep("",3),stringsAsFactors = F)
